---
title: "Usage of Microclim R Api"
author: "Aji John"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage of Microclim R Api}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This API toolkit gives you an easy wasy to interact with microclim.org which is
 microclimatic data repository. One of the important purpose is to do ecological forecasting. This tutorial helps implements a typical usecase to;

- Load the microclimR api
- Download the microclim data
- Run a basic analysis

## Load the required

First things first, install and load the microclim R library

```{r,eval=FALSE}

library(devtools)
devtools::install_github("trenchproject/microclimRapi")

library(microclimRapi)
library(httr)
library(jsonlite)
```

## Get Token

Microclim.org gives a token to a registered user to use its services via APIs. In the account page, you can find your API key and secret.

```{r,eval=FALSE}
  api_token = getToken('07d4d584c04941a25e291feb8881c685','9ef6bbb24a855fbb765f3890e05592f4','localhost:3000/')
```

## Get Token

This API pkg uses extensively Reference Class(RC) feature of R, a setp-up from S4 classes. Behaviour is like other OO languages.

```{r,eval=FALSE}
ma <- microclimRapi:::MicroclimAPI$new(token = api_token,url_mc='http://localhost:3000/')
```

## Prepare Request and Place a request for extraction

```{r,eval=FALSE}
  mr <- microclimRapi:::MicroclimRequest$new(
                  latS = 39.40012200014591,
                  latN=39.92132255884663,
                  lonW=-106.47674560546875,
                  lonE=-105.92193603515625,
                  variable="ALBEDO",
                  shadelevel=0,
                  hod=0,
                  interval=0,
                  aggregation=0,
                  stdate="19810101",
                  eddate="19810128",
                  file="csv")

  # place a request
  ext_req= ma$request(mr)
  print(toJSON(ext_req))
```



## Check on your request

If Request status is 'EMAILED', you can proceed with downloading the data.

```{r,eval=FALSE}
#check the status of your request
ma$status(requestId)
#status 'EMAILED' means job is complete.

```

## Get CSV/netCDF
```{r,eval=FALSE}
#Pull your netCDF
if(ma$status(requestId) == "EMAILED")
{
  
  # place a request to fetch the files
  ftch_req= ma$fetch(requestId)

  # pass the filename
  ncD <-  ma$download(requestId,ftch_req$files[[1]]$Key)

  #File name has request id as part of it
  writeBin(ncD, strsplit(ftch_req$files[[1]]$Key, "/")[[1]][2])
}

```

##Research question - BioPhy Model for a Lizard projecting into future.


```{r,eval=FALSE}
#Describe the model
#Get Air Temperature for a given date range (Tair)
#Get Long wave radiation , Albedo ?
#


```

