---
title: "Usage of Microclim R Api"
author: "Aji John"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage of Microclim R Api}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This API toolkit gives you an easy wasy to interact with microclim.org which is
 microclimatic data repository. One of the important purpose is to do ecological forecasting.

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Load the required

First things first, install and load the microclim R library

```{r}
devtools::install_github("trenchproject/microclimRapi")
library(microclimRapi)
library(httr)
library(jsonlite)
```

## Get Token

Microclim.org gives a token to a registered user to use its services via APIs. In the account page, you can find your API key and secret.

```{r}
  api_token = getToken('07d4d584c04941a25e291feb8881c685','9ef6bbb24a855fbb765f3890e05592f4','localhost:3000/')
```

## Get Token

This API pkg uses extensively Reference Class(RC) feature of R, a setp-up from S4 classes. Behaviour is like other OO languages.

```{r}
ma <- microclimRapi:::MicroclimAPI$new(token = api_token,url_mc='http://localhost:3000/')
```

## Prepare Request and Place a request for extraction

```{r}
  mr <- microclimRapi:::MicroclimRequest$new(
                  latS = 39.40012200014591,
                  latN=39.92132255884663,
                  lonW=-106.47674560546875,
                  lonE=-105.92193603515625,
                  variable="ALBEDO",
                  shadelevel=0,
                  hod=0,
                  interval=0,
                  aggregation=0,
                  stdate="19810101",
                  eddate="19810128",
                  file="csv")

  # place a request
  ext_req= ma$request(mr)
  print(toJSON(ext_req))
```



## Check on your request

If Request status is 'EMAILED', you can proceed with downloading the data.

```{r,echo=FALSE}
#check the status of your request

```

## Get CSV/netCDF
```{r,echo=FALSE}
#Pull your netCDF

```

##Research question - BioPhy Model for a Lizard projecting into future.


```{r,echo=FALSE}
#Describe the model

```

